\textsf{Are large language models superhuman chemists?}

### 2024-10-29 src/tex/appendix.tex
add variables

Larger models generally perform better (\LlamaThreeOneFourZeroFiveBInstruct > \LlamaThreeOneSeventyBInstruct > \LlamaThreeOneEightBInstruct). However, smaller but well-designed models can compete with larger models. For example, \GemmaTwoNineBIt has an overall accuracy of 0.48 on \ChemBench corpus, which is only 10\% less accurate than the much larger \LlamaThreeOneFourZeroFiveBInstruct model.

>>>>

Larger models generally perform better (\LlamaThreeOneFourZeroFiveBInstruct > \LlamaThreeOneSeventyBInstruct > \LlamaThreeOneEightBInstruct). However, smaller but well-designed models can compete with larger models. For example, \GemmaTwoNineBIt has an overall accuracy of \variable{output/trends_section_variables/gemma_9B.txt} on \ChemBench corpus, which is only \variable{output/trends_section_variables/diff_between_llama_405B_and_gemma_9B.txt}\% less accurate than the much larger \LlamaThreeOneFourZeroFiveBInstruct model.
